CDSR Human Data/Modelling Paper

### 2013-09-12 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
JK fixed up figure one and the resized the images files

Section~\ref{sec:cdsrs} discusses the features of CDSRs using illustrative examples.  We claim that (1) people can effectively communicate using these regions, and (2) the size and shape of these regions change with the context.  We argue that to account for this behavior, a cognitive systems solution must respond to changing context, apply learned regions to new contexts, and reuse learned knowledge in multiple tasks.  To explore these claims, we present the results of a human study, in which, people marked regions and rated points representing CDSRs in three different environments in 13 different contexts.  In discussing the results, we consider a number of approaches from current cognitive systems and robotics.  Each approach has a number of shortcomings that must be addressed not only to improve our understanding of human spatial reasoning, but also to enable robust intelligent assistants in human environments.

@@

%Combine these figures into a single figure across
\begin{figure}
\centering
%% Change the classroom to be a picture stimuli
  \begin{subfigure}[b]{0.3\textwidth}
  \includegraphics[width=\textwidth]{figures/classroom.png}
  \caption{\textit{The front of the classroom} could be defined as the area between the desks and the whiteboard where people give presentations.}
  \end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
  \includegraphics[width=\textwidth]{figures/safety-3.jpg}
  \caption{\textit{Safety for the scout} is contextually defined by the location of the friendly turrets and the capabilities of the opposing force.}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
  \includegraphics[width=\textwidth]{figures/bottleneck.JPG}
  \caption{A \textit{bottleneck} occurs when paths are confined to a narrow region by geographic features.  In this case, the water prevents ground movement.}
  \label{fig:safety}
  \end{subfigure}

  \caption{Examples of spatial regions used as stimuli in our experiments.}
  \label{fig:examples}
\end{figure}

>>>>

Section~\ref{sec:cdsrs} discusses the features of CDSRs using illustrative examples.  We claim that (1) people can effectively communicate using these regions, and (2) the size, location and shape of these regions change with the context.  We argue that to account for this behavior, a cognitive systems solution must respond to changing context, apply learned regions to new contexts, and reuse learned knowledge in multiple tasks.  To explore these claims, we present the results of a human study, in which, people marked regions and rated points representing CDSRs in three different environments in 13 different contexts.  In discussing the results, we consider a number of approaches from current cognitive systems and robotics.  Each approach has a number of shortcomings that must be addressed not only to improve our understanding of human spatial reasoning, but also to enable robust intelligent assistants in human environments.

@@

%Combine these figures into a single figure across
\begin{figure}
\centering
%% Change the classroom to be a picture stimuli
\begin{tabular}{c c c} 
  \begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/classroom.png}
%  \caption{\textit{The front of the classroom} could be defined as the area between the desks and the whiteboard where people give presentations.}
  \caption{\textit{The front of the classroom}.}
  \end{subfigure} &
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/safety-3.jpg}
%  \caption{\textit{Safety for the scout} is contextually defined by the location of the friendly turrets and the capabilities of the opposing force.}
  \caption{\textit{The safe region for the scout}.}
\end{subfigure} & 
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/bottleneck.JPG}
%  \caption{A \textit{bottleneck} occurs when paths are confined to a narrow region by geographic features.  In this case, the water prevents ground movement.}
 \caption{\textit{The bottleneck}.}
  \label{fig:safety}
  \end{subfigure}\\
\end{tabular}
  \caption{Examples of spatial regions used as stimuli in our experiments.}
  \label{fig:examples}
\end{figure}
